\documentclass[a4paper,UKenglish,cleveref, autoref, thm-restate]{oasics-v2021}

\pdfoutput=1
\bibliographystyle{plainurl}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\bibliographystyle{plainurl}
\title{Formal Verification Chained Moonshot Byzantine Fault Tolerant State Machine Replication Protocol}
\titlerunning{Formal Verification of Chained Moonshot SMR Protocol}
\author{M.~Praveen}{Chennai Mathematical Institute \and ReLaX}{}{}{Partially funded by a grant from the Infosys foundation}
\author{Issac Doidge}{SupraOracles}{}{}{}
\author{Raghavendra Ramesh}{SupraOracles}{}{}{}
\authorrunning{M.~Praveen, Issac Doidge, Raghavendra Ramesh}
\Copyright{M.~Praveen, Issac Doidge, Raghavendra Ramesh}
\ccsdesc[500]{Networks~Protocol testing and verification}
\ccsdesc[500]{Theory of computation~Logic and verification}
\ccsdesc[500]{Theory of computation~Automated reasoning}
\begin{CCSXML}
	<ccs2012>
	<concept>
	<concept_id>10003033.10003039.10003041.10003042</concept_id>
	<concept_desc>Networks~Protocol testing and verification</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	<concept>
	<concept_id>10003752.10003790.10002990</concept_id>
	<concept_desc>Theory of computation~Logic and verification</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	<concept>
	<concept_id>10003752.10003790.10003794</concept_id>
	<concept_desc>Theory of computation~Automated reasoning</concept_desc>
	<concept_significance>500</concept_significance>
	</concept>
	</ccs2012>
\end{CCSXML}
\keywords{Distributed consensus, Formal verification}
\acknowledgements{We would like to thank Chandradeep Dey and Namrata Reddy, who were part of this project during its initial phase.}
%\nolinenumbers %uncomment to disable line numbering

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

	\maketitle
	\begin{abstract}
Decentralized Finance (DeFi) have emerged as a contemporary competitive as well as complementary to traditional centralized finance systems. As of 23rd January 2024, per Defillama approximately USD 55 billion is the total value locked on the DeFi applications on all blockchains put together.

A Byzantine Fault Tolerant (BFT) State Machine Replication (SMR) protocol, popularly known as consensus protocol, is the central component of a blockchain. Forks in blockchains imply possible double spending attacks and are catastrophic given high volumes of finance that are transacted on blockchains. Formal verification of the safety of BFT SMR protocols provide the highest guarantee possible but is considered as complex and challenging. This is reflected by the fact that not many complex consensus protocols are formally verified except for Tendermint. 

We focus on Chained Moonshot consensus protocol. Similar to Tendermint's formal verification we too model Chained Moonshot using IVy and formally prove that for all network sizes, as long as the number of Byzantine validators is less than the 1/3, the protocol never forks, thus proving that double spending is not possible.
	\end{abstract}
\newcommand{\prcs}{\mathcal{V}}
\newcommand{\blkchn}{\mathbf{B}}

\section{Introduction}
\input{intro}

\section{The Chained Moonshot SMR Protocol}
\input{moonshot-details}
\end{document}